\documentclass[PICOAPC.tex]{subfiles}

\begin{document}
%
% author list table.
% 4 columns, authors + affiliations
%
\LARGE{ \centerline{\bf{PICO: Probe of Inflation and Cosmic Origins}}}
%
%\vskip -16pt
%\Large{ \centerline{Report from a Probe-Scale Mission Study}}
%\Large{ \centerline{July, 2019 }}

\parindent = 0pt

\vspace{4pt}
\large{Thematic Area: Space Based Projects}

\vspace{2pt}
\parindent = 0pt
%\normalsize{
\normalsize{ Lead Author: Shaul Hanany (hanany@umn.edu)\,$^{1}$ } 

\vspace{-0.06in} 

%\normalsize{
%\small{
%Steering Committee: Charles Bennett\,$^{2}$, Scott Dodelson\,$^{3}$, Lyman Page\,$^{4}$ } \\
%\vspace{-6pt} \\
%\normalsize{
%\small{
%\raggedright
% Executive Committee:
% James~Bartlett\,$^{5,6}$,
% Nick~Battaglia\,$^{7}$,
% Jamie~Bock\,$^{8,6}$,
% Julian~Borrill\,$^{9,10}$,
% David~Chuss\,$^{11}$,
% Brendan~P.~Crill\,$^{6}$,
% Jacques~Delabrouille\,$^{5,12}$,
% Mark~Devlin\,$^{13}$,
% Laura~Fissel\,$^{14}$,
% Raphael~Flauger\,$^{15}$,
% Dan~Green\,$^{16}$,
% J.~Colin~Hill\,$^{17,18}$,
% Johannes~Hubmayr\,$^{19}$,
% William~Jones\,$^{4}$,
% Lloyd~Knox\,$^{20}$,
% Al~Kogut\,$^{21}$,
% Charles~Lawrence\,$^{6}$,
% Jeff~McMahon\,$^{22}$,
% Tim~Pearson\,$^{8}$,
% Clem~Pryke\,$^{1}$,
% Marcel~Schmittfull\,$^{18}$,
% Amy~Trangsrud\,$^{6}$,
% Alexander~van~Engelen\,$^{23}$
% \\
% }
\label{authorlist}

\vspace{6pt}

\large  {\centerline {Authors}}
%\vskip 0pt
%
\footnotesize {
% change to left justified
\begin{multicols}{4}
Marcelo Alvarez $^{2,3}$                 \\
Emmanuel Artis $^{4}$                  \\
%Peter Ashton $^{9}$                   \\
Peter Ashton $^{2,3,5}$                    \\
%Peter Ashton $^{24}$                   \\
Jonathan Aumont $^{6}$                 \\
Ragnhild Aurlien $^{7}$                \\
Ranajoy Banerji $^{7}$                 \\
R. Belen Barreiro $^{8}$               \\
James G. Bartlett $^{9,10}$               \\
%James G. Bartlett $^{6}$              \\
Soumen Basak $^{11}$                    \\
Nick Battaglia $^{12}$                  \\
Jamie Bock $^{10,13}$                      \\
%Jamie Bock   !!Caltech then JPL!! $^{6}$   \\
Kimberly K. Boddy $^{14}$               \\
Matteo Bonato $^{15}$                   \\
Julian Borrill $^{2,16}$                  \\
%Julian Borrill $^{10}$                 \\
Fran\c{c}ois Bouchet $^{17}$            \\
Fran\c{c}ois Boulanger $^{18}$          \\
Blakesley Burkhart $^{19}$              \\
Jens Chluba $^{20}$                     \\
David Chuss $^{21}$                     \\
Susan E. Clark $^{22,23}$                  \\
Joelle Cooperrider $^{10}$              \\
Brendan P. Crill $^{10}$                \\
Gianfranco De Zotti $^{24}$             \\
Jacques Delabrouille $^{4,9}$            \\
%Jacques Delabrouille $^{12}$           \\
%Mark Devlin $^{13}$   \\
Eleonora Di Valentino $^{25}$           \\
Joy Didier $^{26}$                      \\
Olivier Dor\'e $^{10,13}$                  \\
%Olivier Dor\'e    !!! JPL then Caltech!!! $^{8}$   \\
Hans K. Eriksen $^{7}$                 \\
Josquin Errard $^{9}$                  \\
Tom Essinger-Hileman $^{27}$            \\
Stephen Feeney $^{28}$                  \\
Jeffrey Filippini $^{29}$               \\
Laura Fissel $^{30}$                    \\
Raphael Flauger $^{31}$                 \\
Unni Fuskeland $^{7}$                  \\
%Vera Gluscevic $^{39}$                  \\
Vera Gluscevic $^{26}$                  \\
Krzysztof M. Gorski $^{10}$             \\
Dan Green $^{3}$                       \\
Shaul Hanany $^{1}$                    \\
Brandon Hensley $^{32}$                 \\
Diego Herranz $^{8}$                   \\
J. Colin Hill $^{22,28}$                   \\
%J. Colin Hill $^{18}$                  \\
Eric Hivon $^{17}$                      \\
Ren\'{e}e  Hlo\v{z}ek $^{33}$           \\
Johannes Hubmayr $^{34}$                \\
Bradley R. Johnson $^{35}$              \\
William Jones $^{32}$                   \\
Terry Jones $^{1}$                     \\
Lloyd Knox $^{36}$                      \\
Al Kogut $^{27}$                        \\
Marcos L\'{o}pez-Caniego $^{37}$        \\
Charles Lawrence $^{10}$                \\
Alex Lazarian $^{38}$                   \\
Zack Li $^{32}$                         \\
Mathew Madhavacheril $^{32}$            \\
%Jeff McMahon $^{22}$   \\
Jean-Baptiste Melin $^{4}$             \\
Joel Meyers $^{39}$                     \\
Calum Murray $^{9}$                    \\
Mattia Negrello $^{40}$                 \\
Giles Novak $^{41}$                     \\
Roger O'Brient $^{10,13}$                  \\
%Roger O'Brient      !!! JPL then Caltech!!! $^{8}$   \\
Christopher Paine $^{10}$               \\
Tim Pearson $^{13}$                     \\
Levon Pogosian $^{42}$                  \\
Clem Pryke $^{1}$                      \\
%Giuseppe Puglisi $^{48}$               \\
Giuseppe Puglisi $^{43,44}$                \\
Mathieu Remazeilles $^{20}$             \\
Graca Rocha $^{10,13}$                     \\
%Graca Rocha $^{8}$                    \\
Marcel Schmittfull $^{22}$              \\
Douglas Scott $^{45}$                   \\
Peter Shirron $^{27}$                   \\
Ian Stephens $^{46}$                    \\
Brian Sutin $^{10}$                     \\
Maurizio Tomasi $^{47}$                 \\
Amy Trangsrud $^{10}$                   \\
Alexander van Engelen $^{48}$           \\
Flavien Vansyngel $^{49}$               \\
Ingunn K. Wehus $^{7}$                 \\
Qi Wen $^{1}$                          \\
Siyao Xu $^{38}$                        \\
Karl Young $^{1}$                      \\
Andrea Zonca $^{50}$
\end{multicols}
}

\vskip -7pt

\large { \centerline {Endorsers}}
%\vskip 0pt
%
\footnotesize {
%\begin{minipage}{1.2\textwidth}
\begin{multicols}{4}
Maximilian Abitbol              \\
Zeeshan Ahmed                   \\
David Alonso                    \\
Mustafa A. Amin                 \\
Adam Anderson                   \\
James Annis                     \\
Jason Austermann                \\
Carlo Baccigalupi               \\
Darcy Barron                    \\
Ritoban Basu Thakur             \\
Elia Battistelli                \\
Daniel Baumann                  \\
Karim Benabed                   \\
Bradford Benson                 \\
Paolo de Bernardis              \\
Marco Bersanelli                \\
Federico Bianchini              \\
Daniel Bilbao-Ahedo             \\
Colin Bischoff                  \\
Sebastian Bocquet               \\
J. Richard Bond                 \\
Jeff Booth                      \\
Sean Bryan                      \\
Carlo Burigana                  \\
Giovanni Cabass                 \\
Robert Caldwell                 \\
John Carlstrom                  \\
Xingang Chen                    \\
Francis-Yan Cyr-Racine          \\
Paolo de Bernardis              \\
Tijmen de Haan                  \\
C. Darren Dowell                \\
Cora Dvorkin                    \\
Chang Feng                      \\
Ivan Soares Ferreira            \\
Aurelien Fraisse                \\
Andrei V. Frolov                \\
Nicholas Galitzki               \\
Silvia Galli                    \\
Ken Ganga                       \\
Tuhin Ghosh                     \\
Sunil Golwala                   \\
Riccardo Gualtieri              \\
Jon E. Gudmundsson              \\
Nikhel Gupta                    \\
Nils Halverson                  \\
Kyle Helson                     \\
Sophie Henrot-Versill\'e        \\
Thiem Hoang                     \\
Kevin M. Huffenberger           \\
Kent Irwin                      \\
Reijo Keskitalo                 \\
Rishi Khatri                    \\
Chang-Goo Kim                   \\
Theodore Kisner                 \\
Arthur Kosowsky                 \\
Ely Kovetz                      \\
Kerstin Kunze                   \\
Guilaine Lagache                \\
Daniel Lenz                     \\
Fran\c{c}ois Levrier            \\
Marilena Loverde                \\
Philip Lubin                    \\
Juan Macias-Perez               \\
Nazzareno Mandolesi             \\
Enrique Mart\'{i}nez-Gonz\'{a}lez   \\
Carlos Martins                  \\
Silvia Masi                     \\
Tomotake Matsumura              \\
Darragh McCarthy                \\
P. Daniel Meerburg              \\
Alessandro Melchiorri           \\
Marius Millea                   \\
Amber Miller                    \\
Joseph Mohr                     \\
Lorenzo Moncelsi                \\
Pavel Motloch                   \\
Tony Mroczkowski                \\
Suvodip Mukherjee               \\
Johanna Nagy                    \\
Pavel Naselsky                  \\
Federico Nati                   \\
Paolo Natoli                    \\
Michael Niemack                 \\
Elena Orlando                   \\
Bruce Partridge                 \\
Marco Peloso                    \\
Francesco Piacentini            \\
Michel Piat                     \\
Elena Pierpaoli   \\
Giampaolo Pisano                \\
Nicolas Ponthieu                \\
Giuseppe Puglisi                \\
Benjamin Racine                 \\
Christian Reichardt             \\
Christophe Ringeval             \\
Karwan Rostem                   \\
Anirban Roy                     \\
Jose Alberto Rubino-Martin      \\
Matarrese Sabino                \\
Maria Salatino                  \\
Benjamin Saliwanchik            \\
Neelima Sehgal                  \\
Sarah Shandera                  \\
Erik Shirokoff                  \\
An\v{z}e Slosar                 \\
Tarun Souradeep                 \\
Suzanne Staggs                  \\
George Stein                    \\
Radek Stompor                   \\
Rashid Sunyaev                  \\
Aritoki Suzuki                  \\
Eric Switzer                    \\
Andrea Tartari                  \\
Grant Teply                     \\
Peter Timbie                    \\
Matthieu Tristram               \\
Caterina Umilt\`{a}             \\
Rien van de Weygaert            \\
Vincent Vennin                  \\
Licia Verde                     \\
Patricio Vielva                 \\
Abigail Vieregg                 \\
Jan Vrtilek                     \\
Benjamin Wallisch               \\
Benjamin Wandelt                \\
Gensheng Wang                   \\
Scott Watson                    \\
Edward J. Wollack               \\
Zhilei Xu                       \\
Siavash Yasini
%Martin White    \\
\end{multicols}
%\end{minipage}
}

\vskip -7pt

\Large  {\centerline {Affiliations}}
\vspace{-6pt}
%
\begin{multicols}{2}
\raggedright
\scriptsize {
%\footnotesize {
1. University of Minnesota - Twin Cities.  \\
2. Lawrence Berkeley National Laboratory.  \\
3. University of California, Berkeley.  \\
4. IRFU, CEA, Universit\'e Paris-Saclay, France.  \\
5. Kavli Institute for the Physics and Mathematics of the Universe (WPI).  \\
6. IRAP, Universit\'e de Toulouse, France.  \\
7. University of Oslo, Norway.  \\
8. Instituto de F\'isica de Cantabria (CSIC-Universidad de Cantabria), Spain.  \\
9. APC, Univ Paris Diderot, CNRS/IN2P3, CEA/lrfu, Obs de Paris, Sorbonne Paris Cit\'e, France.  \\
10. Jet Propulsion Laboratory, California Institute of Technology.  \\
11. School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, India.  \\
12. Cornell University.  \\
13. California Institute of Technology.  \\
14. Johns Hopkins University.  \\
15. INAF-Istituto di Radioastronomia and Italian ALMA Regional Centre, Italy.  \\
16. Space Sciences Laboratory, University of California, Berkeley.  \\
17. Institut d'Astrophysique de Paris, CNRS and Sorbonne Universit\'e, France.  \\
18. Ecole Normale Superieure, Paris, France.  \\
19. Rutgers University.  \\
20. JBCA, University of Manchester.  \\
21. Villanova University.  \\
22. Institute for Advanced Study, Princeton.  \\
23. Hubble Fellow          \\
24. INAF-Osservatorio Astronomico di Padova, Italy.  \\
25. University of Manchester.  \\
26. University of Southern California.  \\
27. NASA Goddard Space Flight Center.  \\
28. Center for Computational Astrophysics, Flatiron Institute.  \\
29. University of Illinois, Urbana-Champaign.  \\
30. National Radio Astronomy Observatory.  \\
31. University of California, San Diego.  \\
32. Princeton University.  \\
33. Department of Astronomy \& Astrophysics and Dunlap Institute, University of Toronto, Canada.  \\
34. National Institute of Standards and Technology.  \\
35. Columbia University.  \\
36. University of California, Davis.  \\
37. European Space Astronomy Centre.  \\
38. University of Wisconsin - Madison.  \\
39. Southern Methodist University.  \\
40. Cardiff University School of Physics and Astronomy.  \\
41. Northwestern University.  \\
42. Simon Fraser University.  \\
43. Stanford University.  \\
44. Kavli Institute for Particle Astrophysics and Cosmology.  \\
45. University of British Columbia, Canada.  \\
46. Harvard-Smithsonian Center for Astrophysics.  \\
47. Universit\`a degli studi di Milano.  \\
48. Canadian Institute for Theoretical Astrophysics, University of Toronto, Canada.  \\
49. Institut d'Astrophysique Spatiale, CNRS, Univ. Paris-Sud, Universit\'e Paris-Saclay, France.  \\
50. San Diego Supercomputer Center, University of California, San Diego.

%3. Carnegie Melon University.  \\
%13. University of Pennsylvania.  \\
%22. University of Michigan.  \\

}
\end{multicols}

\vskip -7pt

\end{document}
